Detailed Chemical Abundances with \tc

### 2015-09-08 article/ms.tex
Test

\usepackage{amsmath,amsbsy}

@@

\section{Appendix A: Reproducing this research}
This article has been compiled from the `git` repository hosted online at GitHub (commit hash `x` on `master` branch). The figures and tables included in this article can be reproduced in full using the following commands in a modern terminal:

>>>>

\usepackage{amsmath,amsbsy}
\usepackage{gitinfo2}

@@

\section{Appendix A: Reproducing this research}
This article has been compiled from the `git` repository hosted online at GitHub (commit hash \gitHash on `master` branch). The figures and tables included in this article can be reproduced in full using the following commands in a modern terminal:
